\tableofcontents

\section{Acknowledgements}
I would like to take this opportunity to say a genuine and heart-felt thank you to the many people who helped me on the way to finally completing this thesis.

Firstly, of course, I thank my supervisor Professor Roy Sambles. The road to this thesis hasn't always been easy, but Roy has helped me put things into perspective on more than one occasion, and for that I am truly grateful. It has not only been your ability to instantly spot the solution to my problems, but also your ability to instantly spot when I've been surfing rather than in the lab, that has kept me on my toes throughout the last three years. Thank you.

Secondly, I must say a special thank you to Stephen Cornford. If it were not for both your immense understanding of liquid crystal dynamics and your immense ability to explain complex problems to me in a way in which I can understand, this Ph.D would not have been possible. Your razor sharp wit has also not gone un-noticed. I must also apologise for the barrage of messages you received once I'd started writing up this thesis, when I was having a panic attack almost daily. Thank you Steph.

I must also say a special thank you to the displays team at Hewlett Packard Labs in Bristol. I gratefully acknowledge the genuine interest and help that I received at our CASE meetings. I can honestly say that I felt welcome and part of the team almost instantly. A special mention must go to Tim Taphouse for being an all round source of technical expertise as well as being a fantastic mentor, and also to Steve Kitson for always taking the time to help out and always providing the solution to the problem at hand. Fantastic input was almost always provided by everyone in the group with particular reference to Adrian Geisow and Chris Newton. Of course, the ECLC 2011 in Slovenia would not have been as enjoyable without the `mothering' provided by Suzanna Klein and the perpetual moaning provided by Rob `hang-time' Greasty. Thank you.

A big thank you must also go to Benny Hallam for being very understanding in giving me time to finish writing when I started work in Cornwall.

Next, as is customary, I would like to thank the more senior members of the Electromagnetic Materials Group at Exeter. Firstly, what can I say? Matthew (Lockers, Lockertron, Stocker, LockHeart) Lockyear RCE. Perhaps the less said here the better. Just remember this, `\textit{what's said in the water, stays in the water}'. Next I must say thank you to Alistair `Hello there' Hibbins for all the comic moments and home-brew help. I can't wait to see what you cook up for the next Great Physics Beer Festival. Thank you to Ian `Hoop-dream' Hooper NRC. For you I have just one question, just one, it's a question that everyone is dyeing to know the answer too, something that I haven't been brave enough to ask you over the last three years ................... vodka ball? A special thank you also to both Fuzi and Lizhen, whether we were discussing my previous girlfriends, or a bowl of 2000 year old soup from an ancient chinese grave, I was always having fun. Sharon Jewell for all the help and advice at the start of my `three years', it's fair to say that you taught me almost everything I know about making liquid crystal cells, and you were right, about 1 in 4 did work! Tim Atherton for your `long range' helpful conversations, listening ear and computational expertise! Euan Hendry for regularly taking all my money in late night poker sessions. Pete V for the sound life advice and that one good surf at Putsborough, hopefully we'll get in again sometime. Bill Barnes for not only being an all round source of help, but for being my first tutor as an undergraduate physicist and firmly setting me on the path to continuing in Physics. Andy Murray for tea time chat and that one good surf at Dawlish Warren, keep it up (the sea will get warmer in the summer)! Tomeck for all the figure conversion that you made possible. Much appreciated! Evgenny Sirotkin for being a fantastic Russian role model. I've never known anyone with a stronger hand shake or a firmer hug and pat on the back. Tom Isaac for being a source of much humour and good will, and to Nick Cole, without you I wouldn't have any samples or any shiny metal things to play with. We started at near enough the same day, and I have to say it's gone very fast, but thank you for all the technical expertise and advice. I must also say a big thank you to Alan Usher for agreeing to be my mentor at such short notice, and after just one meeting, helping me feel much better about my Ph. D.

Throughout my undergraduate time at Exeter, I made some great friends in Physics that also went on to complete their Ph. Ds here at Exeter. These are Lemmy Steve, Chris `Buzza' Burrows and James Edmunds. So I must say a big thank you to you guys for helping me through my time here as a Ph. D student. In particular Lemmy Steve for all the good years as MPhys lab partners and hopefully many more good years to come!

Next I come to a special section of my acknowledgements. Team Basement. When I first started my Ph. D, a select few were chosen to dwell in the basement of the Physics department. Without natural light, cleanliness, or a chance of escape, we forged a special bond that many basement dwellers before us have also shared. So I must say a massive thank you to the original Team Basement for helping to keep me sane and providing me with some of the best memories of my time at Exeter. James Parsons, Caroline `\textit{Simon, side step to your left}' Pouya (aka Jupiter) and Edmund Stone. Ed, I must say a special thank you for not actually killing me, and for all the help with R during the early days. You were a fantastic human drum kit and I hope our friendship continues long after our time at Exeter! Caroline I must also say thank you for expanding my musical horizons and making me a better all round individual. Maybe someday you'll like Radiohead?

Along with Team Basement, there were many new Ph. D starters in 2008. Over the last three years I feel I've made good friendships with all of you and would like to say a big thank you to Matt `Biggatronic' Bigginton, you adonis! Mel Taylor, for helping me calm down when I started to panic about this thesis. Celia Butler for being an all round source of information and help, I'd love to go gliding some day. Last but not least, a special mention must go to Helen Rance RC for eating all my chocolate bourbons and teaching me how to cook, a bit. 

Also, during my three years as a post graduate student, I have met many new starters. Unfortunately we haven't been able to spend a long time together, but I would like to say thank you to Dmitry Polyushkin, Lizzy Brock, Simon Berry, Chinna Devarapu (you have the best laugh in the world!), Al Murray, Matt Nixon, Tim Starkey RC and Joe Blackman, who made me realise that not everything is lost! 

Who am I missing? I'm sure I'm missing someone important...oh yes! That's right, Alfred John Lethbridge. Well, what can I say? It seems strange to acknowledge you, since we are in fact the same person, but, `\textit{sometimes....not always....but sometimes}'. Seriously, thanks for the sound advice and brilliant memories over the last two years. See you in China.

Penultimately I would like to thank The Stormers with which I had the insurmountable pleasure of living (and working) with for 2 years. Namely, Dr. Ciaran `Stewstorm' Stewart RC, Thomas `Constorm' Constant RC and Peter `Halestorm' Hale. Ciaran, you are a fantastic chef and a fantastic person. Thank you for all the bacon sandwiches and cups of tea. Not only that, but for all the surfing memories and BBQs at Radstations. I will, forever, remember the day of ball-ache. Tom, you are in some ways, the epitamy of what a Stormer should be. A gentleman and a scholar. Thanks for the t-shirt which i'll never wear again, and maybe someday you'll be the subject of an award winning National Geographic photo. Finally Pete, i'm writing this with my chordorouy trousers on. Perhaps we should make the angle again? Definitely DON'T come in (thanks for the tea).

Finally I'd like to say a huge thank you to my Mum, Dad and Brother. If it wasn't for the science open day at Ridgeway school all those years ago, I may never have experienced the joy of watching a ping pong ball being levitated by a jet of air from a vacuum cleaner in reverse. That means I may have never developed an interest in Physics! But seriously, thank you for the constant love, support, help and advice.